Self Referencing Sequences

### 2014-10-26 draft.tex
added more stuff

@@

\begin{theorem} If $1<a<b$ then the self-referencing sequence beginning with $a$ generated over $\{1, a, b\}$ and the self-referencing sequence beginning with $b$ generated over $\{1, a, b\}$ are independent.
\end{theorem}
\begin{proof}
We proceed by contradiction. If the two sequences are not independent then they must differ by some minimal prefix of length $n$. If we let $a_i$ be the sequence beginning with $a$ and $b_i$ be the sequence beginning with $b$ the
\begin{equation*}
a_{n+k} = b_{k}.
\end{equation*}
We know that the first $b$ terms of the sequence which begins with a $b$ are $b$'s. Because $b>a>1$ no block can be longer then $b$. Thus the terms immediately preceding and following this block in the sequence $a_i$ must not be $b$'s. Because of this the first block of $b_i$ is the $m+1$th block of $a_i$, where $m$ is some positive integer. Since the value of the sequence at position $k$ is also the length of the $k$th block this means that $a_{m+1}=b_1$. In fact the $k$th block of $b_i$ is the $(m+k)$th block of $a_i$ and so 
\begin{equation*}
a_{m+k} = b_k
\end{equation*}

@@

\section{Equivalence}
\label{equivalence}

@@

>>>>

We claim that a self-referencing sequence is uniquely determined by the generating set and the starting number. To see why this is true, we can simply give an algorithm to build the sequence. Assume the generating set is $\{a_1,a_2,\dots,a_m\}$ and that we start with some $a_i$.

\textbf{Algorithm:}
Assume that the sequence $\{s\}$ is initially just $a_i$. At the next step, add an additional $a_i -1$ repetitions of $a_i$ to the end of the sequence. Now if there is a second term in the sequence, read that term and write down that many copies of $a_{i+1}$. If there is no term, write down $a_{i+1}$.

NEED TO FINISH THIS.

Since we know that a self-referencing sequence is uniquely determined by the generating set and the starting number, we introduce the notation $s(A,a)$ to denote the unique sequence generated by set $A$ with starting number $a \in A$.

@@

\begin{theorem}
\label{independentsequences}
If $1<a<b$ then the self-referencing sequence beginning with $a$ generated over $\{1, a, b\}$ and the self-referencing sequence beginning with $b$ generated over $\{1, a, b\}$ are independent.
\end{theorem}
\begin{proof}
We proceed by contradiction. If the two sequences are not independent then they must differ by some minimal prefix of length $n$. If we let $a_i$ be the sequence beginning with $a$ and $b_i$ be the sequence beginning with $b$ the
\begin{equation*}
a_{n+k} = b_{k}.
\end{equation*}
We know that the first $b$ terms of the sequence which begins with a $b$ are $b$'s. Because $b>a>1$ no block can be longer then $b$. Thus the terms immediately preceding and following this block in the sequence $a_i$ must not be $b$'s. Because of this the first block of $b_i$ is the $m+1$th block of $a_i$, where $m$ is some positive integer. Since the value of the sequence at position $k$ is also the length of the $k$th block this means that $a_{m+1}=b_1$. In fact the $k$th block of $b_i$ is the $(m+k)$th block of $a_i$ and so 
\begin{equation*}
a_{m+k} = b_k
\end{equation*}

@@

\section{Equivalence}
\label{equivalence}
\emph{Written by Fermi Ma, edited by Perry Kleinhenz and Erik Waingarten}

In this section, we consider a slightly weaker definition of equivalence. Consider, for example, sequences generated by $\{1,2,3\}$. Theorem~\ref{independentsequences} shows that the sequence starting with 2
\begin{align*}
2,2,3,3,1,1,1,2,2,2,3,1,2,3,3,1,1,2,2,3,3,3,\dots
\end{align*}
and the sequence starting with 3
\begin{align*}
3,3,3,1,1,1,2,2,2,3,1,2,3,3,1,1,2,2,3,3,3,\dots
\end{align*}
are independent in the sense that neither sequence is exactly contained in the other. However, if we delete the first two numbers of the sequence starting with 2, and the first number of the sequence starting with 3, we get 
\begin{align*}
3,3,1,1,1,2,2,2,3,1,2,3,3,1,1,2,2,3,3,3,\dots
\end{align*}
in both cases. (Need to further justify why these two are the same, probably with a reading distance argument)

Thus, since both sequences are essentially the same if certain prefixes are removed, we call these sequences \emph{equivalent}. To formalize, this, we say that two sequences $\{a_i\}$ and $\{b_i\}$ are equivalent if there exists some integers $n,k \geq 0$ such that
\begin{align*}
a_{n+i} = b_{k+i}
\end{align*}

We now give the following conjecture

\begin{conjecture} Any sequence generated by a set $S$ is equivalent to any other sequence generated by the same set $S$.
\end{conjecture}

This conjecture is partly motivated by the fact that the property holds for $\{1,2,3\}$. For generating sets with larger numbers, we have been unable to verify or refute the conjecture. However, in Section~\ref{Density}, we show that the starting number of a sequence does not affect the densities of each number, which provides some evidence for this conjecture.

@@

We change focus in this section and consider how to generate self-referential sequences with an iterative process. We first look at the sequences generated by $\{1,2\}$.

One possible iterative process is as follows. Let the sequence $\{s^0\}$ be 2, and let the sequence $\{s^{(i)}\}$ for $i \geq 1$ be the unique sequence that starts with 2 and is such that its block lengths, read from left to right, reproduce the sequence $\{s^{(i-1)}\}$. This gives:
\begin{align*}
\{s^{(0)}\} &= 2\\
\{s^{(1)}\} &= 2,2\\
\{s^{(2)}\} &= 2,2,1,1\\
\{s^{(3)}\} &= 2,2,1,1,2,1\\
\{s^{(4)}\} &= 2,2,1,1,2,1,2,2,1\\
&\cdots
\end{align*}
Let $s^\infty$ be the limit of this process. We claim that $s^\infty$ is the unique self-referential sequence $s(\{1,2\},2)$ generated by $\{1,2\}$ with starting number 2.
\begin{proof}
We show that this is true by simply showing that if $s^{(i)}$ is a prefix of
\end{proof}
